\chapter{Usability testing procedure}\label{app:evaluation-script}

\section*{Introduction and consent}
\begin{enumerate}
\item \textbf{Meet participant} and introduce yourself and project.
\item Explain the \textbf{purpose of the testing} and it's role within
  the academic project assessment. The tests are for the product, not
  of the participant.
\item Request \textbf{permission to record} audio and screen capture
  the testing device. The purpose of the recordings are to prevent me
  from having to transcribe everything that is said as it is
  happening.
\item Request permission for recording to be \textbf{distributed as
  evidence} of usability testing if required.
\end{enumerate}

\section*{Testing introduction}
\begin{enumerate}
\item \textbf{Start recording}.
\item Ask for a brief overview of the \textbf{participant's
  background}, and what they're studying.
\item Ascertain the participant's understanding of the relevant
  \textbf{science background and terminology}.
\item Ascertain the participant's \textbf{familiarity with the
  dataset}. Any prior knowledge of the project should be stated here.
\item \textbf{Demonstrate} to the participant how to use the testing
  device.
\item \textbf{Thinking aloud} - provide a hands on demonstration of
  thinking aloud using the Aston website. Show how you would navigate
  to find out how to apply for a research degree in CS department.
\end{enumerate}

\newpage

\section*{Testing}
\begin{enumerate}
\item \textbf{First impressions} - bring up the website on the testing
  device and hand over controls to participant.
\item \textbf{Present task list} to the participant and explain why it
  exists. Unlike many websites, pip-db is a specific tool to be used
  to answer questions and perform specific searches, so it is helpful
  to have a set of staged questions rather than letting the user
  browse indiscriminately.
\item \textbf{Work through tasks} - Give a spoken introduction to each
  one, and ask that the participant says out loud which step they are
  working on.
\end{enumerate}

\section*{Post-test}
\begin{enumerate}
\item What is your \textbf{overall impression} of the site?
\item Would you \textbf{use the website} for tasks like those you
  worked through?
\item \textbf{How likely} do you see yourself performing a task like
  those you worked through under normal conditions?
\item If you were to \textbf{change one thing} about the website, what
  would it be?
\item \textbf{Score out of 10}.
\end{enumerate}

\section*{End of session}
\begin{enumerate}
\item \textbf{Thank participant} for their time and cooperation.
\item Any closing \textbf{thoughts or questions}?
\item \textbf{Stop recording}.
\end{enumerate}