\bibitem{NCBIND} National Center for Biotechnology Information. About
  NCBI. NCI. [Online] ND. [Cited: 31st October 2013.]
  \url{http://blast.ncbi.nlm.nih.gov/Blast.cgi}.

\bibitem{Maier1983} Maier, D. The Theory of Relational Databases. Computer
  Science press, 1983.

\bibitem{DDG1999} Drug Design Group. AntiJen Database:
  Homepage. AntiJen. [Online] 1999. [Cited: 10th December 2013.]
  \url{http://www.ddg-pharmfac.net/antijen/AntiJen/antijenhomepage.htm}.

\bibitem{DDGND} Drug Design Group. DSD: dehydrogenase stereospecificities
  database. DSD. [Online] ND. [Cited: 10th December 2013.]
  \url{http://www.ddg-pharmfac.net/dsd/DSD/dehydrog.htm}.

\bibitem{DDGNDa} Drug Design Group. PPD database. PPD a database of protein
  ioinization constants. [Online] ND. [Cited: 10th December 2013.]
  \url{http://www.ddg-pharmfac.net/ppd/PPD/pKahomepage.htm}.

\bibitem{EclipseND} The Eclipse Foundation. OpenUP. Introduction to
  OpenUP. [Online] ND. [Cited: 31st October 2013.]
  \url{http://epf.eclipse.org/wikis/openup/}.

\bibitem{Rational2011} Rational. Rational Unified Process - Best Practices for
  Software Development Teams. IBM. [Online] November 2011. [Cited: 21st October
    2013.]
  \url{http://www.ibm.com/developerworks/rational/library/content/03July/1000/1251/1251_bestpractices_TP026B.pdf}.

\bibitem{FSF1991} Free Software Foundation, Inc. GNU General Public License,
  version 2. GNU Operating System. [Online] June 1991. [Cited: 31st October
    2013.] \url{http://www.gnu.org/licenses/gpl-2.0.html}.

\bibitem{Cummins2013} Cummins, C. pip-db: Bioinformatics search engine for
  protein isoelectric points. GitHub. [Online] 14th October 2013. [Cited: 31st
    October 2013.]  \url{https://github.com/ChrisCummins/pip-db}.

\bibitem{Martin2011} Martin, R. C. Agile Software Development, Principles,
  Patterns, and Practices. Pearson, 2011.
