\newpage
\section{RISK ASSESSMENT \hrulefill}

Table 1 lists some of the potential project risks that were identified during
the initial research phase which could influence the success of the project and
its ability to meet the objectives and deliverables. For each risk, the
probability of it occurring and impact it would have on the project have been
assigned a value between 1 and 5 to indicate their magnitude.

\begin{table}[H]
\centering
\begin{tabular}{ | l | l | l || c | c | }
\hline
Risk & Description & Category & Probability & Impact\\
\hline
R1  & Design is not intuitive                           & Design       & 2 & 3\\
R2  & Project involves use of new technical skills      & Development  & 5 & 5\\
R3  & High Level of technical complexity                & Development  & 5 & 3\\
R4  & Complex deployment of production website          & Development  & 5 & 4\\
R5  & Project milestones not clearly defined            & Planning     & 1 & 1\\
R6  & System requirements not adequately identified     & Requirements & 2 & 5\\
R7  & Change in project requirements during development & Requirements & 1 & 5\\
R8  & Changes in dataset format during development      & Resources    & 2 & 5\\
R9  & Unable to obtain required resources               & Resources    & 1 & 1\\
R10 & Users not committed to the project                & Users        & 2 & 4\\
R11 & Lack of cooperation from users                    & Users        & 1 & 4\\
R12 & Users with negative attitudes toward the project  & Users        & 1 & 2\\
\hline
\end{tabular}
\caption{A list of potential project risks and their severity}
\label{tab:risk-assessment}
\end{table}

\subsection{Mitigation Strategies}

For each of the risks discovered in the assessment, mitigation strategies have
been defined which provide techniques to avoid or minimise the threat of each
risk.

\paragraph{Design is not intuitive} the key to mitigation of this risk is in frequent and
effective user testing and an understanding of typical and common use-cases for
the product.

\paragraph{Project involves use of new technical skills} in order to prevent this risk
from having a serious impact on the project, it will be necessary to begin
studying and reading about the technologies that will be used at a very early
stage in the project, long before the start of the implementation.

\paragraph{High Level of technical complexity} avoiding this risk will involve ensuring
that the scope of the project remains technically feasible, and that the
software architecture is abstracted into small enough units that it is easier to
focus on each one separately, as well as keeping small iterative development
cycles and adequate test coverage to prevent regressions when implementing new
functionality.

\paragraph{Complex deployment of production website} a website with independent
data and application logic components can result in an intricate deployment
process. This is a common problem in the development of complex web application,
where development and production environments must be synchronised and
differences between debugging and releases builds must be accounted for. In
order to mitigate this risk, a suite of tools to configure, build and deploy the
website should be developed at an early stage, allowing for fast deployment of
public releases.

\paragraph{Project milestones not clearly defined} a thoroughly described and well
thought out project plan will help to prevent scheduling issues and delays in
development that would arise from this risk.

\paragraph{System requirements not adequately identified} a comprehensive specification
of the finished product before implementation begins will help to mitigate this
risk.

\paragraph{Change in project requirements during development} an agile approach towards
accommodating for changes in the requirements should be used so as to keep the
time between user feedback sessions and input from stakeholders low.

\paragraph{Changes in dataset form at during development} it is not possible to entirely
avoid this risk due its nature and the dependence on third parties, but steps
can be taken to prevent any delays that this would cause, chiefly, a well
abstracted data parsing component which can be switched and modified if
necessary to accommodate for a new dataset format.

\paragraph{Unable to obtain required resources} since the project does not require many
resources, it is important to acquire these as early on in the development
process as possible, and alternative resources should be planned for, such as
local test servers.

\paragraph{Users not committed to the project, lack of cooperation from users,
  and users with negative attitudes toward the project} the useful of the
finished project will depend largely on ensuring that the needs of the users are
considered the primary goals of the design. Violating this principle may cause
disillusionment from the people who are volunteering their time to assist in the
project.
