\chapter{Conclusions}\label{chap:conclusions}

%% This is mandatory. The conclusion is the third most important
%% section of the document. Briefly restate the work done; summarise
%% any findings or recommendations emerging from the project. Everyone
%% who reads your report will read the conclusion.

The web application described in this document entirely fulfils the
stated goal of categorising and providing accessible online search
functionality for PIP-DB. In addition to satisfying the core
deliverables, a pragmatic approach to the development of
infrastructure and tooling has resulted in the creation of several
supporting projects, including the YAPS file format, pipbot repository
manager, plausible nonsense generator, and CSV analyser. Additionally,
contributions have been made to four popular existing open source
projects as a result of development: watch-less, clojure-koans,
sqlkorma, and gitstats.

The pip-db repository contains 34,205 lines of code, with an estimated
development time of 605 hours, based on the 2,420 revisions in the
version control history (based on an assumed average time cost of 15
minutes of development per revision). While costly in terms of time,
the radical switch in programming language after the completion of the
initial prototype allowed for a rare direct comparison to be made
between non-trivial software written in PHP and Clojure. The
comparison can be used for qualitative evaluation of the strengths of
both languages, and results showed that the reimplementation in a
functional language resulted in a 75\% reduction in code base size for
functionally identical web server implementations
\cite{cummins2014migrating}.

Development of an Autotooled build system for websites showed how
shell-level parallelism could be used to reduce execution times by a
factor of 5. Further work on the build system could reduce these times
further by enabling parallelism within the core of automake. It is
possible to repurpose the build system for future web application
projects.

It my recommendation that further usability tests be performed on the
existing pip-db design before any modifications are made to the user
interface. While defended by some \cite{nielsen2000you}, it is
generally believed that a usability testing sample size of 5 is too
small to reveal an adequate number of usability problems
\cite{spool2001testing, woolrych2001and}. Further work on the pip-db
website could include the development of administrative tools for
modifying data, and refinements to the performance and security of the
web server implementation. Increased scalability could be provided by
implementing multi-threading support for request handling, and greater
edge case handling could increase the server's robustness. One
overlooked aspect of pip-db is the user account and registration
system. The implementation of an accounts system was left incomplete
as time was devoted instead to the implementation of novel features
and user interaction refinements. The persistent storage component of
pip-db could be the subject of future research, with NoSQL
technologies finding increasing usage for the similar purposes of
document storage \cite{tudorica2011comparison, mongo2014leading,
  hecht2011nosql, mongo2013top5}. Using a NoSQL store in place of the
existing PostgreSQL back-end would remove the need for the
vectorisation of YAPS records and greatly simply the data upload
logic.
