\chapter{The website}

\section{Design}

Describe with justification the general structure of your experiment,
design, or program and explain how it satisfies the project
requirements. All major design decisions should be described,
including the evaluation of alternatives and the justification for the
chosen approach (it is not sufficient to simply say “I did it this
way”). For programs, include any human-computer interface that the
system involves. Diagrams and examples are important.

\section{Implementation}

Give a high-level overview of your realisation of the design. Further
description may be given of any particularly noteworthy aspects,
e.g. specialised circuits or algorithms, but avoid excessive low-level
detail — see the section below on design or program
documentation. Diagrams and examples are important. Describe
experimental results, or design or program testing methods and their
outcomes.

\section{Evaluation}

Realistic evaluation is a vital part of a good project
report. Describe evaluation methods; discuss reliability and usability
of the end-product; where appropriate, obtain client views.  To what
extent have the specified objectives of the project been met? How
successful and appropriate was the method adopted?  As in any
engineering report, this section should also include an evaluation of
the project costs.  Make sure that the costing includes manpower
(i.e. your own time as the “principal investigator” and that of any
“consultants” you have had to refer to for help or advice, such as the
supervisor, moderator, or support staff).

\subsection{Suggestions for further work}

Acknowledge any limitations of the work and give any suggestions for
further work. Again, this is a vital part of a good project report.
