\newpage
\begin{thebibliography}{9}
\bibitem{IBMRUP} Wikipedia (ND). IBM Rational Unified Process.
  \url{http://en.wikipedia.org/wiki/IBM\_Rational\_Unified\_Process}.
\bibitem{Kulbertis2011} Kulbertis, B (2011). Synchronizing a MySQL Database with
  Git and Git
  Hooks. \url{http://ben.kulbertis.org/2011/10/synchronizing-a-mysql-database-with-git-and-git-hooks/}.
\bibitem{Buvrilovic2013} Cubrilovic, N (2013). Facebook PHP Source Code from
  August 2007. GitHubGist. \url{https://gist.github.com/nikcub/3833406}.
\bibitem{Rakowski2011} Rakowski, K. Getting Started With PHP
  Templating. Smashing
  Magazine. \url{http://coding.smashingmagazine.com/2011/10/17/getting-started-with-php-templating/}.
\bibitem{Cummins2013} Cummins, C (2013). Emu - a snapshot backup
  program. GitHub. \url{https://github.com/ChrisCummins/emu}.
\bibitem{Cummins2013a} Cummins, C (2013). t4 - a tool for generating tests as
shell scripts from m4 macros. GitHub. \url{https://github.com/ChrisCummins/t4}.
\bibitem{SeleniumND} Selenium (ND). SeleniumHQ Browser
Automation. \url{http://docs.seleniumhq.org/}.
\bibitem{HolowaychukND} Holowaychuck, T. D. (ND). Mocha - simple, flexible, fun
javascript test framework for node.js \& the browser. (BDD, TDD, QUnit styles
via interfaces. GitHub. \url{https://github.com/visionmedia/mocha}.
\bibitem{HolowaychukNDa} Holowaychuck, T. J. Should.js - BDD style assertions
for node.js -- test framework
agnostic. GitHub. \url{https://github.com/visionmedia/should.js}.
\bibitem{Clemson2010} Clemson, T (2010). Blog rolling with mongoDB, express and
Node.js. How to Node. \url{http://howtonode.org/express-mongodb}.
\bibitem{CoursewareND} Courseware (ND). Real Time Web with Node.js. Courseware
code school. \url{http://courseware.codeschool.com/node_slides.pdf}.
\bibitem{Webapplog2013} Webappllog (2013). PHP
vs. Node.js. \url{http://webapplog.com/php-vs-node-js/}.
\bibitem{Sperry2013} Sperry, B. (2013). ionicons - The premium icon font for
Ionic Framework. GitHub. \url{https://github.com/driftyco/ionicons}
\bibitem{WordPressND} Wordpress (ND). Database
Description. \url{http://codex.wordpress.org/Database_Description}.
\bibitem{WordPressNDa} WordPress (ND). WordPress
APIs. \url{http://codex.wordpress.org/WordPress_APIs}.
\bibitem{Kimsal2011} Kimsal, M. (2011). PHP is not object oriented! Michael Kimsal's
weblog. \url{http://michaelkimsal.com/blog/php-is-not-object-oriented/}.
\bibitem{Rakowski2011} Rakowski, K. (2011). Getting Started with PHP
Templating. Smashing Magazine.
\url{http://coding.smashingmagazine.com/2011/10/17/getting-started-with-php-templating/}.
\bibitem{Saltman2013} Saltman, D. B. (2013). Stop doing this crap on your
startups website. harknesslabls.
\url{http://harknesslabs.com/post/66570723467/stop-doing-this-crap-on-your-startups-website}.
\bibitem{Loire2012} Loire, I. (2012). Building web apps with node.js, socket.io,
knockout.js and zombie.js - Codemotion 2012. slideshare.
\url{http://www.slideshare.net/iloire/building-web-apps-with-nodejs-socketio-knockoutjs-and-zombiejs-codemotion-2012}.
\bibitem{SheetJS2013} SheetJS (2013). SheetJS In-Browser Live Grid Demo
\url{http://oss.sheetjs.com/}.
\bibitem{Butler2010} Butler, T. (2010). MVC in PHP tutorial part 1: Hello
World. \url{http://r.je/mvc-in-php.html}.
\bibitem{Butler2012} Butler, T. (2012). Are Static Methods/Variables bad
practice? \url{http://r.je/static-methods-bad-practice.html}.
\bibitem{Hevery2008} Hevery, M. (2008). Guide: Writing Testable
Code. \url{http://misko.hevery.com/code-reviewers-guide/}.
\bibitem{Rodrigue2012} Rodrigue, St. (2012).  Dependency Injection in
PHP. nettuts+.
\url{http://net.tutsplus.com/tutorials/php/dependency-injection-in-php/}.
\bibitem{SensioLabsND} SensioLabs (ND). The Dependency Injection
Component. Symfony.
\url{http://symfony.com/doc/2.0/components/dependency_injection/introduction.html}.
\bibitem{SQLiteND} SQLite (ND). How SQLite is
Tested. \url{http://www.sqlite.org/testing.html}.
\end{thebibliography}
